---
title: "tree"
author: "Trista Cheng"
date: "6/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(dplyr)
library(tidyverse)
library(rpart)
library(rpart.plot)
library(MASS)
library(Metrics)
library(randomForest)
library(ROCR)
library(fitdistrplus)
```

```{r}
my_data <- read_excel("Yarn Dyeing Data analysis_0616_v2.xlsx")
```

```{r}
class(my_data)  
str(my_data) # make sure the variables are correctly defined.
summary(my_data) # a quick summary of each variable
```

```{r}
my_data_1 <- my_data[, c(1,2,3,6,8:24,26,27,28,30)]
#my_data_1 <- my_data
#my_data_2 = my_data_1 %>% drop_na()  # 删除NA会筛走很多缺失部分流程的生产任务
str(my_data_1)
```

```{r}
my_data_1$Machine_Name <- as.factor(my_data_1$Machine_Name)
my_data_1$Batch_Type <- as.factor(my_data_1$Batch_Type)
my_data_1$Colorist <- as.factor(my_data_1$Colorist)
my_data_1$Remark_label <- as.factor(my_data_1$Remark_label)
my_data_1$ColorOnly <- as.factor(my_data_1$ColorOnly)
my_data_1$Colorist_Type <- as.factor(my_data_1$Colorist_Type)
my_data_1$Pre_Art_No <- as.factor(my_data_1$Pre_Art_No)
my_data_1$Dye_Art_No <- as.factor(my_data_1$Dye_Art_No)
my_data_1$After_Art_No <- as.factor(my_data_1$After_Art_No)
my_data_1$Fix_Art_No <- as.factor(my_data_1$Fix_Art_No)
my_data_1$Fabric <- as.factor(my_data_1$Fabric)
my_data_1$Is_Repair <- as.factor(my_data_1$Is_Repair)
#str(my_data_1)

library(data.table)
# replace all NA in character column to 0
factor_cols = c("Machine_Name", "Batch_Type", "Colorist", "Remark_label", "ColorOnly", "Colorist_Type", "Pre_Art_No", "Dye_Art_No", "After_Art_No", "Fix_Art_No","Fabric","Is_Repair")
for (col in factor_cols) set(my_data_1, which(is.na(my_data_1[[col]])), col, "0")

# replace all NA in numeric columns to 0
num_cols = c("Pre_Art_Actual_Time", "Dye_Art_Actual_Time", "Dye_Art_Sample_Time", "After_Art_Actual_Time", "After_Art_Sample_Time", "Fix_Art_Actual_Time", "Fix_Art_Sample_Time")
for (col in num_cols) set(my_data_1, which(is.na(my_data_1[[col]])), col, 0)

my_data_2 <- my_data_1
my_data_2$pure_dye <- my_data_2$Dye_Art_Actual_Time - my_data_2$Dye_Art_Sample_Time
my_data_2$pure_after <- my_data_2$After_Art_Actual_Time - my_data_2$After_Art_Sample_Time
my_data_2$pure_fix <- my_data_2$Fix_Art_Actual_Time - my_data_2$Fix_Art_Sample_Time
str(my_data_2)
```

```{r}
#arrange(count(my_data_1, "Machine_Name"), desc(freq))
#arrange(count(my_data_1, "Colorist"), desc(freq))
#arrange(count(my_data_1, "Pre_Art_No"), desc(freq))
#arrange(count(my_data_1, "After_Art_No"), desc(freq))
```




# Create train/test sets


```{r}
set.seed(123)
smp_siz = floor(0.95*nrow(my_data_2)) 
train_ind = sample(seq_len(nrow(my_data_2)),size = smp_siz)  # Randomly identifies therows equal to sample size ( defined in previous instruction) from  all the rows of Smarket dataset and stores the row number in train_ind
data_train= my_data_2[train_ind,] #creates the training dataset with row numbers stored in train_ind
data_test = my_data_2[-train_ind,]  # creates the test dataset excluding the row numbers mentioned in train_ind
```

```{r}
my_data_3 <- data_test
```

### S1: Pre_Art_Actual_Time

# Linear regression
```{r}
lm_s1 <- lm(Pre_Art_Actual_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
# summary(lm_s1)
```

```{r}
data_train$pred_lm_s1 <- predict(lm_s1, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Pre_Art_No[i] == 0){ 
        data_train$pred_lm_s1[i] = 0
    }
}

#rmse_lm_s1 <- rmse(my_data_3$pred_lm_s1, my_data_3$Pre_Art_Actual_Time)
```


```{r}
my_data_3$pred_lm_s1 <- predict(lm_s1, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Pre_Art_No[i] == 0){ 
        my_data_3$pred_lm_s1[i] = 0
    }
}

rmse_lm_s1 <- rmse(my_data_3$pred_lm_s1, my_data_3$Pre_Art_Actual_Time)
```



# Regression tree
```{r}
t_pre_art <- rpart(Pre_Art_Actual_Time ~.,
            data = data_train,         # check importance with complete set
            method = "anova",         # indicates the outcome is continuous
            control = rpart.control(
                       minsplit = 1,  # min number of obs for a split 
                       minbucket = 1, # min no of obs in terminal nodes
                       cp=0)          #decrease in complex for a split 
)
t_pre_art$variable.importance
```

```{r}
reg.tree_s1 <- rpart(Pre_Art_Actual_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair , data = data_train)
summary(reg.tree_s1)

##rpart.plot(reg.tree_s1, type = 4, tweak = 2)

reg.tree_s1$variable.importance

printcp(reg.tree_s1)  # displays table of fits across complexity parameter values

#rsq.rpart(reg.tree_s1)  # plots approximate R-squared and relative error for different splits
```

```{r}
data_train$pred_rt_s1 <- predict(reg.tree_s1, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Pre_Art_No[i] == 0){ 
        data_train$pred_rt_s1[i] = 0
    }
}

#rmse_rt_s1 <- rmse(my_data_3$pred_rt_s1, my_data_3$Pre_Art_Actual_Time)
```

```{r}
my_data_3$pred_rt_s1 <- predict(reg.tree_s1, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Pre_Art_No[i] == 0){ 
        my_data_3$pred_rt_s1[i] = 0
    }
}

rmse_rt_s1 <- rmse(my_data_3$pred_rt_s1, my_data_3$Pre_Art_Actual_Time)
```

# Random Forest
```{r}
my_data_2.rf_s1 <- randomForest(Pre_Art_Actual_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train, ntree = 1000, na.action=na.roughfix) 
```

```{r}
data_train$pred_rf_s1 <- predict(my_data_2.rf_s1, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Pre_Art_No[i] == 0){ 
        data_train$pred_rf_s1[i] = 0
    }
}

#rmse_rf_s1 <- rmse(my_data_3$pred_rf_s1, my_data_3$Pre_Art_Actual_Time)
```

```{r}
my_data_3$pred_rf_s1 <- predict(my_data_2.rf_s1, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Pre_Art_No[i] == 0){ 
        my_data_3$pred_rf_s1[i] = 0
    }
}

rmse_rf_s1 <- rmse(my_data_3$pred_rf_s1, my_data_3$Pre_Art_Actual_Time)
```



### S2: Dye_Art_Actual_Time (excl dye_art_sample_time)

# Linear regression
```{r}
lm_s2 <- lm(pure_dye ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
# summary(lm_s2)
```

```{r}
data_train$pred_lm_s2 <- predict(lm_s2, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Dye_Art_No[i] == 0){ 
        data_train$pred_lm_s2[i] = 0
    }
}

#rmse_lm_s2 <- rmse(my_data_3$pred_lm_s2, my_data_3$pure_dye)
```

```{r}
my_data_3$pred_lm_s2 <- predict(lm_s2, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Dye_Art_No[i] == 0){ 
        my_data_3$pred_lm_s2[i] = 0
    }
}

rmse_lm_s2 <- rmse(my_data_3$pred_lm_s2, my_data_3$pure_dye)
```

# Regression tree
```{r}
t_pure_dye <- rpart(pure_dye ~.,
            data = data_train,         # check importance with complete set
            method = "anova",         # indicates the outcome is continuous
            control = rpart.control(
                       minsplit = 1,  # min number of obs for a split 
                       minbucket = 1, # min no of obs in terminal nodes
                       cp=0)          #decrease in complex for a split 
)
t_pure_dye$variable.importance
```

```{r}
reg.tree_s2 <- rpart(pure_dye ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
summary(reg.tree_s2)

#rpart.plot(reg.tree_s2, type = 4, tweak = 1)

reg.tree_s2$variable.importance

printcp(reg.tree_s2)  # displays table of fits across complexity parameter values

#rsq.rpart(reg.tree_s2)  # plots approximate R-squared and relative error for different splits
```
```{r}
data_train$pred_rt_s2 <- predict(reg.tree_s2, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Dye_Art_No[i] == 0){ 
        data_train$pred_rt_s2[i] = 0
    }
}

#rmse_rt_s2 <- rmse(my_data_3$pred_rt_s2, my_data_3$pure_dye)
```

```{r}
my_data_3$pred_rt_s2 <- predict(reg.tree_s2, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Dye_Art_No[i] == 0){ 
        my_data_3$pred_rt_s2[i] = 0
    }
}

rmse_rt_s2 <- rmse(my_data_3$pred_rt_s2, my_data_3$pure_dye)
```

# Random Forest
```{r}
my_data_2.rf_s2 <- randomForest(pure_dye ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train, ntree = 1000, na.action=na.roughfix) 
# deleted Machine_name, colorist and coloronly as more than 53 levels in either factor

```

```{r}
data_train$pred_rf_s2 <- predict(my_data_2.rf_s2, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Dye_Art_No[i] == 0){ 
        data_train$pred_rf_s2[i] = 0
    }
}

#rmse_rf_s2 <- rmse(data_train$pred_rf_s2, data_train$pure_dye)
```

```{r}
my_data_3$pred_rf_s2 <- predict(my_data_2.rf_s2, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Dye_Art_No[i] == 0){ 
        my_data_3$pred_rf_s2[i] = 0
    }
}

rmse_rf_s2 <- rmse(my_data_3$pred_rf_s2, my_data_3$pure_dye)
```


### S3: Dye_Art_Sample_Time

# Linear regression
```{r}
lm_s3 <- lm(Dye_Art_Sample_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
# summary(lm_s3)
```

```{r}
data_train$pred_lm_s3 <- predict(lm_s3, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Dye_Art_No[i] == 0){ 
        data_train$pred_lm_s3[i] = 0
    }
}

#rmse_lm_s3 <- rmse(my_data_3$pred_lm_s3, my_data_3$Dye_Art_Sample_Time)
```

```{r}
my_data_3$pred_lm_s3 <- predict(lm_s3, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Dye_Art_No[i] == 0){ 
        my_data_3$pred_lm_s3[i] = 0
    }
}

rmse_lm_s3 <- rmse(my_data_3$pred_lm_s3, my_data_3$Dye_Art_Sample_Time)
```

# Regression tree
```{r}
t_dye_sample <- rpart(Dye_Art_Sample_Time ~.,
            data = data_train,         # check importance with complete set
            method = "anova",         # indicates the outcome is continuous
            control = rpart.control(
                       minsplit = 1,  # min number of obs for a split 
                       minbucket = 1, # min no of obs in terminal nodes
                       cp=0)          #decrease in complex for a split 
)
t_dye_sample$variable.importance
```

```{r}
reg.tree_s3 <- rpart(Dye_Art_Sample_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
summary(reg.tree_s3)

#rpart.plot(reg.tree_s3, type = 4, tweak = 1)

reg.tree_s3$variable.importance

printcp(reg.tree_s3)  # displays table of fits across complexity parameter values

#rsq.rpart(reg.tree_s3)  # plots approximate R-squared and relative error for different splits
```
```{r}
data_train$pred_rt_s3 <- predict(reg.tree_s3, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Dye_Art_No[i] == 0){ 
        data_train$pred_rt_s3[i] = 0
    }
}

#rmse_rt_s3 <- rmse(my_data_3$pred_rt_s3, my_data_3$Dye_Art_Sample_Time)
```

```{r}
my_data_3$pred_rt_s3 <- predict(reg.tree_s3, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Dye_Art_No[i] == 0){ 
        my_data_3$pred_rt_s3[i] = 0
    }
}

rmse_rt_s3 <- rmse(my_data_3$pred_rt_s3, my_data_3$Dye_Art_Sample_Time)
```


# Random Forest
```{r}
my_data_2.rf_s3 <- randomForest(Dye_Art_Sample_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train, ntree = 1000, na.action=na.roughfix) 

```

```{r}
data_train$pred_rf_s3 <- predict(my_data_2.rf_s3, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Dye_Art_No[i] == 0){ 
        data_train$pred_rf_s3[i] = 0
    }
}

#rmse_rf_s3 <- rmse(data_train$pred_rf_s3, data_train$Dye_Art_Sample_Time)
```

```{r}
my_data_3$pred_rf_s3 <- predict(my_data_2.rf_s3, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Dye_Art_No[i] == 0){ 
        my_data_3$pred_rf_s3[i] = 0
    }
}

rmse_rf_s3 <- rmse(my_data_3$pred_rf_s3, my_data_3$Dye_Art_Sample_Time)
```


### S4: After_Art_Actual_Time (excl after_art_sample_time)

# Linear regression
```{r}
lm_s4 <- lm(pure_after ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
# summary(lm_s4)
```

```{r}
data_train$pred_lm_s4 <- predict(lm_s4, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$After_Art_No[i] == 0){ 
        data_train$pred_lm_s4[i] = 0
    }
}

#rmse_lm_s4 <- rmse(my_data_3$pred_lm_s4, my_data_3$pure_after)
```

```{r}
my_data_3$pred_lm_s4 <- predict(lm_s4, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$After_Art_No[i] == 0){ 
        my_data_3$pred_lm_s4[i] = 0
    }
}

rmse_lm_s4 <- rmse(my_data_3$pred_lm_s4, my_data_3$pure_after)
```



# Regression tree
```{r}
t_pure_after <- rpart(pure_after ~.,
            data = data_train,         # check importance with complete set
            method = "anova",         # indicates the outcome is continuous
            control = rpart.control(
                       minsplit = 1,  # min number of obs for a split 
                       minbucket = 1, # min no of obs in terminal nodes
                       cp=0)          #decrease in complex for a split 
)
t_pure_after$variable.importance
```

```{r}
reg.tree_s4 <- rpart(pure_after ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
summary(reg.tree_s4)

#rpart.plot(reg.tree_s4, type = 4, tweak = 2)

reg.tree_s4$variable.importance

printcp(reg.tree_s4)  # displays table of fits across complexity parameter values

#rsq.rpart(reg.tree_s4)  # plots approximate R-squared and relative error for different splits
```
```{r}
data_train$pred_rt_s4 <- predict(reg.tree_s4, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$After_Art_No[i] == 0){ 
        data_train$pred_rt_s4[i] = 0
    }
}

#rmse_rt_s4 <- rmse(my_data_3$pred_rt_s4, my_data_3$pure_after)
```

```{r}
my_data_3$pred_rt_s4 <- predict(reg.tree_s4, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$After_Art_No[i] == 0){ 
        my_data_3$pred_rt_s4[i] = 0
    }
}

rmse_rt_s4 <- rmse(my_data_3$pred_rt_s4, my_data_3$pure_after)
```




# Random Forest
```{r}
my_data_2.rf_s4 <- randomForest(pure_after ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train, ntree = 1000,na.action=na.roughfix) 

```

```{r}
data_train$pred_rf_s4 <- predict(my_data_2.rf_s4, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$After_Art_No[i] == 0){ 
        data_train$pred_rf_s4[i] = 0
    }
}

#rmse_rf_s4 <- rmse(my_data_3$pred_rf_s4, my_data_3$pure_after)
```

```{r}
my_data_3$pred_rf_s4 <- predict(my_data_2.rf_s4, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$After_Art_No[i] == 0){ 
        my_data_3$pred_rf_s4[i] = 0
    }
}

rmse_rf_s4 <- rmse(my_data_3$pred_rf_s4, my_data_3$pure_after)
```

### S5: After_Art_Sample_Time

# Linear regression
```{r}
lm_s5 <- lm(After_Art_Sample_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
# summary(lm_s5)
```

```{r}
data_train$pred_lm_s5 <- predict(lm_s5, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$After_Art_No[i] == 0){ 
        data_train$pred_lm_s5[i] = 0
    }
}

#rmse_lm_s5 <- rmse(my_data_3$pred_lm_s5, my_data_3$After_Art_Sample_Time)
```

```{r}
my_data_3$pred_lm_s5 <- predict(lm_s5, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$After_Art_No[i] == 0){ 
        my_data_3$pred_lm_s5[i] = 0
    }
}

rmse_lm_s5 <- rmse(my_data_3$pred_lm_s5, my_data_3$After_Art_Sample_Time)
```


# Regression tree
```{r}
t_after_sample <- rpart(After_Art_Sample_Time ~.,
            data = data_train,         # check importance with complete set
            method = "anova",         # indicates the outcome is continuous
            control = rpart.control(
                       minsplit = 1,  # min number of obs for a split 
                       minbucket = 1, # min no of obs in terminal nodes
                       cp=0)          #decrease in complex for a split 
)
t_after_sample$variable.importance
```

```{r}
reg.tree_s5 <- rpart(After_Art_Sample_Time ~  Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
summary(reg.tree_s5)

#rpart.plot(reg.tree_s5, type = 4, tweak = 2)

reg.tree_s5$variable.importance

printcp(reg.tree_s5)  # displays table of fits across complexity parameter values

#rsq.rpart(reg.tree_s5)  # plots approximate R-squared and relative error for different splits
```
```{r}
data_train$pred_rt_s5 <- predict(reg.tree_s5, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$After_Art_No[i] == 0){ 
        data_train$pred_rt_s5[i] = 0
    }
}

#rmse_rt_s5 <- rmse(my_data_3$pred_rt_s5, my_data_3$After_Art_Sample_Time)
```

```{r}
my_data_3$pred_rt_s5 <- predict(reg.tree_s5, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$After_Art_No[i] == 0){ 
        my_data_3$pred_rt_s5[i] = 0
    }
}

rmse_rt_s5 <- rmse(my_data_3$pred_rt_s5, my_data_3$After_Art_Sample_Time)
```

# Random Forest
```{r}
my_data_2.rf_s5 <- randomForest(After_Art_Sample_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train, ntree = 1000, na.action=na.roughfix) 
# deleted Machine_name, colorist and coloronly as more than 53 levels in either factor

```

```{r}
data_train$pred_rf_s5 <- predict(my_data_2.rf_s5, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$After_Art_No[i] == 0){ 
        data_train$pred_rf_s5[i] = 0
    }
}

#rmse_rf_s5 <- rmse(my_data_3$pred_rf_s5, my_data_3$After_Art_Sample_Time)
```

```{r}
my_data_3$pred_rf_s5 <- predict(my_data_2.rf_s5, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$After_Art_No[i] == 0){ 
        my_data_3$pred_rf_s5[i] = 0
    }
}

rmse_rf_s5 <- rmse(my_data_3$pred_rf_s5, my_data_3$After_Art_Sample_Time)
```

### S6: Fix_Art_Actual_Time (excl fix_art_sample_time)

# Linear regression
```{r}
lm_s6 <- lm(pure_fix ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
# summary(lm_s6)
```

```{r}
data_train$pred_lm_s6 <- predict(lm_s6, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Fix_Art_No[i] == 0){ 
        data_train$pred_lm_s6[i] = 0
    }
}

#rmse_lm_s6 <- rmse(my_data_3$pred_lm_s6, my_data_3$pure_fix)
```

```{r}
my_data_3$pred_lm_s6 <- predict(lm_s6, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Fix_Art_No[i] == 0){ 
        my_data_3$pred_lm_s6[i] = 0
    }
}

rmse_lm_s6 <- rmse(my_data_3$pred_lm_s6, my_data_3$pure_fix)
```

# Regression tree
```{r}
t_pure_fix <- rpart(pure_fix ~.,
            data = data_train,         # check importance with complete set
            method = "anova",         # indicates the outcome is continuous
            control = rpart.control(
                       minsplit = 1,  # min number of obs for a split 
                       minbucket = 1, # min no of obs in terminal nodes
                       cp=0)          #decrease in complex for a split 
)
t_pure_fix$variable.importance
```

```{r}
reg.tree_s6 <- rpart(pure_fix ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
summary(reg.tree_s6)

#rpart.plot(reg.tree_s6, type = 4, tweak = 2)

reg.tree_s6$variable.importance

printcp(reg.tree_s6)  # displays table of fits across complexity parameter values

#rsq.rpart(reg.tree_s6)  # plots approximate R-squared and relative error for different splits
```
```{r}
data_train$pred_rt_s6 <- predict(reg.tree_s6, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Fix_Art_No[i] == 0){ 
        data_train$pred_rt_s6[i] = 0
    }
}

#rmse_rt_s6 <- rmse(my_data_3$pred_rt_s6, my_data_3$pure_fix)
```

```{r}
my_data_3$pred_rt_s6 <- predict(reg.tree_s6, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Fix_Art_No[i] == 0){ 
        my_data_3$pred_rt_s6[i] = 0
    }
}

rmse_rt_s6 <- rmse(my_data_3$pred_rt_s6, my_data_3$pure_fix)
```

# Random Forest
```{r}
my_data_2.rf_s6 <- randomForest(pure_fix ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train, ntree = 1000, na.action=na.roughfix) 

```

```{r}
data_train$pred_rf_s6 <- predict(my_data_2.rf_s6, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Fix_Art_No[i] == 0){ 
        data_train$pred_rf_s6[i] = 0
    }
}

#rmse_rf_s6 <- rmse(my_data_3$pred_rf_s6, my_data_3$pure_fix)
```

```{r}
my_data_3$pred_rf_s6 <- predict(my_data_2.rf_s6, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Fix_Art_No[i] == 0){ 
        my_data_3$pred_rf_s6[i] = 0
    }
}

rmse_rf_s6 <- rmse(my_data_3$pred_rf_s6, my_data_3$pure_fix)
```


### S7: Fix_Art_Sample_Time

# Linear regression
```{r}
lm_s7 <- lm(Fix_Art_Sample_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
# summary(lm_s7)
```

```{r}
data_train$pred_lm_s7 <- predict(lm_s7, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Fix_Art_No[i] == 0){ 
        data_train$pred_lm_s7[i] = 0
    }
}

#rmse_lm_s7 <- rmse(my_data_3$pred_lm_s7, my_data_3$Fix_Art_Sample_Time)
```

```{r}
my_data_3$pred_lm_s7 <- predict(lm_s7, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Fix_Art_No[i] == 0){ 
        my_data_3$pred_lm_s7[i] = 0
    }
}

rmse_lm_s7 <- rmse(my_data_3$pred_lm_s7, my_data_3$Fix_Art_Sample_Time)
```

# Regression tree
```{r}
t_fix_sample <- rpart(Fix_Art_Sample_Time ~.,
            data = data_train,         # check importance with complete set
            method = "anova",         # indicates the outcome is continuous
            control = rpart.control(
                       minsplit = 1,  # min number of obs for a split 
                       minbucket = 1, # min no of obs in terminal nodes
                       cp=0)          #decrease in complex for a split 
)
t_fix_sample$variable.importance
```

```{r}
reg.tree_s7 <- rpart(Fix_Art_Sample_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
summary(reg.tree_s7)

#rpart.plot(reg.tree_s7, type = 4, tweak = 1)

reg.tree_s7$variable.importance

printcp(reg.tree_s7)  # displays table of fits across complexity parameter values

#rsq.rpart(reg.tree_s7)  # plots approximate R-squared and relative error for different splits
```
```{r}
data_train$pred_rt_s7 <- predict(reg.tree_s7, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Fix_Art_No[i] == 0){ 
        data_train$pred_rt_s7[i] = 0
    }
}

#rmse_rt_s7 <- rmse(my_data_3$pred_rt_s7, my_data_3$Fix_Art_Sample_Time)
```

```{r}
my_data_3$pred_rt_s7 <- predict(reg.tree_s7, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Fix_Art_No[i] == 0){ 
        my_data_3$pred_rt_s7[i] = 0
    }
}

rmse_rt_s7 <- rmse(my_data_3$pred_rt_s7, my_data_3$Fix_Art_Sample_Time)
```

# Random Forest
```{r}
my_data_2.rf_s7 <- randomForest(Fix_Art_Sample_Time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train, ntree = 1000, na.action=na.roughfix) 

```

```{r}
data_train$pred_rf_s7 <- predict(my_data_2.rf_s7, newdata = data_train)

for (i in 1:nrow(data_train)){
    if (data_train$Fix_Art_No[i] == 0){ 
        data_train$pred_rf_s7[i] = 0
    }
}

#rmse_rf_s7 <- rmse(my_data_3$pred_rf_s7, my_data_3$Fix_Art_Sample_Time)
```

```{r}
my_data_3$pred_rf_s7 <- predict(my_data_2.rf_s7, newdata = my_data_3)

for (i in 1:nrow(my_data_3)){
    if (my_data_3$Fix_Art_No[i] == 0){ 
        my_data_3$pred_rf_s7[i] = 0
    }
}

rmse_rf_s7 <- rmse(my_data_3$pred_rf_s7, my_data_3$Fix_Art_Sample_Time)
```

### S8: delta time

# Linear regression
```{r}
lm_s8 <- lm(delta_time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
# summary(lm_s7)
```

```{r}
data_train$pred_lm_s8 <- predict(lm_s8, newdata = data_train)
data_train$pred_lm_s8[is.na(data_train$pred_lm_s8)] <- 0
#rmse_lm_s7 <- rmse(my_data_3$pred_lm_s7, my_data_3$Fix_Art_Sample_Time)
```

```{r}
my_data_3$pred_lm_s8 <- predict(lm_s8, newdata = my_data_3)

rmse_lm_s8 <- rmse(my_data_3$pred_lm_s8, my_data_3$delta_time)
rmse_lm_s8
```

# Regression tree
```{r}
t_fix_sample <- rpart(delta_time ~.,
            data = data_train,         # check importance with complete set
            method = "anova",         # indicates the outcome is continuous
            control = rpart.control(
                       minsplit = 1,  # min number of obs for a split 
                       minbucket = 1, # min no of obs in terminal nodes
                       cp=0)          #decrease in complex for a split 
)
t_fix_sample$variable.importance
```

```{r}
reg.tree_s8 <- rpart(delta_time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train)
summary(reg.tree_s8)

#rpart.plot(reg.tree_s7, type = 4, tweak = 1)

reg.tree_s8$variable.importance

printcp(reg.tree_s8)  # displays table of fits across complexity parameter values

#rsq.rpart(reg.tree_s7)  # plots approximate R-squared and relative error for different splits
```
```{r}
data_train$pred_rt_s8 <- predict(reg.tree_s7, newdata = data_train)
data_train$pred_rt_s8[is.na(data_train$pred_rt_s8)] <- 0
#rmse_rt_s7 <- rmse(my_data_3$pred_rt_s7, my_data_3$Fix_Art_Sample_Time)
```

```{r}
my_data_3$pred_rt_s8 <- predict(reg.tree_s8, newdata = my_data_3)


rmse_rt_s8 <- rmse(my_data_3$pred_rt_s8, my_data_3$delta_time)
rmse_rt_s8
```

# Random Forest
```{r}
my_data_2.rf_s8 <- randomForest(delta_time ~ Remark_label + Pre_Art_No + Dye_Art_No + After_Art_No + Fix_Art_No + Colorist + DyestuffUsage + Dyeing_Ratio + Dye_Weight + Machine_Name + ColorOnly + Fabric + Is_Repair, data = data_train, ntree = 1000, na.action=na.roughfix) 

```

```{r}
data_train$pred_rf_s8 <- predict(my_data_2.rf_s8, newdata = data_train)
data_train$pred_rf_s8[is.na(data_train$pred_rf_s8)] <- 0
#rmse_rf_s7 <- rmse(my_data_3$pred_rf_s7, my_data_3$Fix_Art_Sample_Time)
```

```{r}
my_data_3$pred_rf_s8 <- predict(my_data_2.rf_s8, newdata = my_data_3)

rmse_rf_s8 <- rmse(my_data_3$pred_rf_s8, my_data_3$delta_time)
```


# Compare RMSE
```{r}
# Choose the model with the smallest RMSE at each stage
checking_1 <- c(rmse_lm_s1, rmse_rt_s1, rmse_rf_s1)
print(paste("stage 1 chooses:", which(checking_1 == min(checking_1))))
checking_2 <- c(rmse_lm_s2, rmse_rt_s2, rmse_rf_s2)
print(paste("stage 2 chooses:", which(checking_2 == min(checking_2))))
checking_3 <- c(rmse_lm_s3, rmse_rt_s3, rmse_rf_s3)
print(paste("stage 3 chooses:", which(checking_3 == min(checking_3))))
checking_4 <- c(rmse_lm_s4, rmse_rt_s4, rmse_rf_s4)
print(paste("stage 4 chooses:", which(checking_4 == min(checking_4))))
checking_5 <- c(rmse_lm_s5, rmse_rt_s5, rmse_rf_s5)
print(paste("stage 5 chooses:", which(checking_5 == min(checking_5))))
checking_6 <- c(rmse_lm_s6, rmse_rt_s6, rmse_rf_s6)
print(paste("stage 6 chooses:", which(checking_6 == min(checking_6))))
checking_7 <- c(rmse_lm_s7, rmse_rt_s7, rmse_rf_s7)
print(paste("stage 7 chooses:", which(checking_7 == min(checking_7))))
checking_8 <- c(rmse_lm_s8, rmse_rt_s8, rmse_rf_s8)
print(paste("stage 8 chooses:", which(checking_8 == min(checking_8))))
```

```{r}
# Combined model with lowest RMSE at each stage
pred_comb_total <- my_data_3$pred_rf_s1 + my_data_3$pred_rf_s2 + my_data_3$pred_rf_s3 + my_data_3$pred_rf_s4 + my_data_3$pred_rt_s5 + my_data_3$pred_rf_s6 + my_data_3$pred_rf_s7
+ my_data_3$pred_rf_s8
```

```{r}
# Create 5 random testing sets
set.seed(33)
ran <- runif(nrow(my_data_2)) # generate uniform random numbers
data_test_1 <- data.frame(my_data_2[ran < 0.2,])
data_test_2 <- my_data_2[ran > 0.2 & ran < 0.4,]
data_test_3 <- my_data_2[ran > 0.4 & ran < 0.6,]
data_test_4 <- my_data_2[ran > 0.6 & ran < 0.8,]
data_test_5 <- my_data_2[ran > 0.8,]
```







# Aggregation: Total_actual_time
```{r}
## POINT TESTING - total time ## 这里不对 模型不能直接加总
# randomly select 1 sample from test set


# Linear regression model
my_data_3$pred_lm_total <- my_data_3$pred_lm_s1 + my_data_3$pred_lm_s2 + my_data_3$pred_lm_s3 + my_data_3$pred_lm_s4 + my_data_3$pred_lm_s5 + my_data_3$pred_lm_s6 + my_data_3$pred_lm_s7


# Regression tree
my_data_3$pred_rt_total <- my_data_3$pred_rt_s1 + my_data_3$pred_rt_s2 + my_data_3$pred_rt_s3 + my_data_3$pred_rt_s4 + my_data_3$pred_rt_s5 + my_data_3$pred_rt_s6 + my_data_3$pred_rt_s7 + my_data_3$pred_rt_s8


# Random Forest
my_data_3$pred_rf_total <- my_data_3$pred_rf_s1 + my_data_3$pred_rf_s2 + my_data_3$pred_rf_s3 + my_data_3$pred_rf_s4 + my_data_3$pred_rf_s5 + my_data_3$pred_rf_s6 + my_data_3$pred_rf_s7 + my_data_3$pred_rf_s8


# Combined model
my_data_3$pred_comb_total <- my_data_3$pred_rf_s1 + my_data_3$pred_rf_s2 + my_data_3$pred_lm_s3 + my_data_3$pred_rf_s4 + my_data_3$pred_rf_s5 + my_data_3$pred_rf_s6 + my_data_3$pred_rf_s7 + my_data_3$pred_rf_s8

# test one row from test set
testsample <- my_data_3[sample(1:nrow(my_data_3), 1, replace = FALSE),]
print(paste("Actual time of the selected sample:", testsample$Total_Actual_Time))
print(paste("Linear regression predicted time:", round(testsample$pred_lm_total, 2)))
print(paste("Regression tree predicted time:", round(testsample$pred_rt_total, 2)))
print(paste("Random forest predicted time:", round(testsample$pred_rf_total, 2)))
print(paste("Combined model predicted time:", round(testsample$pred_comb_total, 2)))
```

```{r}
data_train$pred_lm_total <- data_train$pred_lm_s1 + data_train$pred_lm_s2 + data_train$pred_lm_s3 + data_train$pred_lm_s4 + data_train$pred_lm_s5 + data_train$pred_lm_s6 + data_train$pred_lm_s7 + data_train$pred_lm_s8


# Regression tree
data_train$pred_rt_total <- data_train$pred_rt_s1 + data_train$pred_rt_s2 + data_train$pred_rt_s3 + data_train$pred_rt_s4 + data_train$pred_rt_s5 + data_train$pred_rt_s6 + data_train$pred_rt_s7 + data_train$pred_rt_s8


# Random Forest
data_train$pred_rf_total <- data_train$pred_rf_s1 + data_train$pred_rf_s2 + data_train$pred_rf_s3 + data_train$pred_rf_s4 + data_train$pred_rf_s5 + data_train$pred_rf_s6 + data_train$pred_rf_s7 + data_train$pred_rf_s8
```


```{r}
residuals_lm <- my_data_3$Total_Actual_Time - my_data_3$pred_lm_total
#plot(residuals_lm)
#hist(residuals_lm,breaks=80)
print(paste("test residuals_lm:",sqrt(sum(residuals_lm^2)/nrow(my_data_3))))

residuals_rt <- my_data_3$Total_Actual_Time - my_data_3$pred_rt_total
#plot(residuals_rt)
#hist(residuals_rt,breaks=80)
print(paste("test residuals_rt:",sqrt(sum(residuals_rt^2)/nrow(my_data_3))))

residuals_rf <- my_data_3$Total_Actual_Time - my_data_3$pred_rf_total
#plot(residuals_rf)
#hist(residuals_rf,breaks=80)
print(paste("test residuals_rf:", sqrt(sum(residuals_rf^2)/nrow(my_data_3))))
```

```{r}
residuals_lm_trn <- data_train$Total_Actual_Time - data_train$pred_lm_total
#plot(residuals_lm)
#hist(residuals_lm,breaks=80)
print(paste("train residuals_lm_trn:",sqrt(sum(residuals_lm_trn^2)/nrow(data_train))))

residuals_rt_trn <- data_train$Total_Actual_Time - data_train$pred_rt_total
#plot(residuals_rt)
#hist(residuals_rt,breaks=80)
print(paste("train residuals_rt_trn:",sqrt(sum(residuals_rt_trn^2)/nrow(data_train))))

residuals_rf_trn <- data_train$Total_Actual_Time - data_train$pred_rf_total
#plot(residuals_rf)
#hist(residuals_rf,breaks=80)
print(paste("train residuals_rf_trn:", sqrt(sum(residuals_rf_trn^2)/nrow(data_train))))
```

```{r}
#mean absolute percentage error
mape(my_data_3$Total_Actual_Time,my_data_3$pred_lm_total)
mape(my_data_3$Total_Actual_Time,my_data_3$pred_rt_total)
mape(my_data_3$Total_Actual_Time,my_data_3$pred_rf_total)
```


```{r}
sqrt(sum(residuals_lm^2)/nrow(my_data_3))
sqrt(sum(residuals_rt^2)/nrow(my_data_3))
sqrt(sum(residuals_rf^2)/nrow(my_data_3))
```


```{r}
# test#
print("test residuals:")
quantile(residuals_lm,  probs = c(10,25,75,90)/100)
quantile(residuals_rt,  probs = c(10,25,75,90)/100)
quantile(residuals_rf,  probs = c(10,25,75,90)/100)
```


```{r}
# train#
print("train residuals:")
quantile(residuals_lm_trn,  probs = c(10,25,75,90)/100)
quantile(residuals_rt_trn,  probs = c(10,25,75,90)/100)
quantile(residuals_rf_trn,  probs = c(10,25,75,90)/100)
```


```{r}
#test#
new_res <- residuals_rt - mean(residuals_rt)

#plot(new_res)
print("rt 90mins:")
length(new_res[new_res<90&new_res>-90])/length(new_res)
length(new_res[new_res<60&new_res>-60])/length(new_res)
length(new_res[new_res<30&new_res>-30])/length(new_res)
new_res <- residuals_lm - mean(residuals_lm)

#plot(new_res)
print("lm 90mins:")
length(new_res[new_res<90&new_res>-90])/length(new_res)
length(new_res[new_res<60&new_res>-60])/length(new_res)
length(new_res[new_res<30&new_res>-30])/length(new_res)
new_res_rf <- residuals_rf - mean(residuals_rf)

#plot(new_res_rf)
print("rf 90mins:")
length(new_res_rf[new_res_rf<90&new_res_rf>-90])/length(new_res_rf)
length(new_res_rf[new_res_rf<60&new_res_rf>-60])/length(new_res_rf)
print("rf 30mins:")
length(new_res_rf[new_res_rf<30&new_res_rf>-30])/length(new_res_rf)
```


```{r}
#train#
new_res_rf_trn <- residuals_rf_trn - mean(residuals_rf_trn)

#plot(new_res_rf)
length(new_res_rf_trn[new_res_rf_trn<90&new_res_rf_trn>-90])/length(new_res_rf_trn)
length(new_res_rf_trn[new_res_rf_trn<30&new_res_rf_trn>-30])/length(new_res_rf_trn)
```


```{r}
my_data_3$residuals_lm <- residuals_lm
my_data_3$residuals_rt <- residuals_rt
my_data_3$residuals_rf <- residuals_rf
```

```{r}
data_train$residuals_lm_trn <- residuals_lm_trn
data_train$residuals_rt_trn <- residuals_rt_trn
data_train$residuals_rf_trn <- residuals_rf_trn
```


```{r}
#write.csv(my_data_3,"test_pred.csv")
#write.csv(data_train,"train_pred.csv")
```

